---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# IOBR: Immune Oncology Bioinformatics Research

IOBR is a R package to perform Tumor microenvironment evaluation, signature estimation.

## Main advantages:
- Provides functionality to estimate signature score (PCA, ssGSEA or z-score)
- Integrated prevalent methodologies to deconvolute microenvironment, such as CIBERSORT, EPIC, ESTIMATE, xCell
- Functions to visulize TME data.
- Identify TME relevant signatures.
- Functions to perform batch analyses for prognostic and predictive biomarkers

The package is not yet on CRAN. You can install from Github:

```{r eval=F, echo=T}
# install.packages("devtools")
devtools::install_github("DongqiangZeng0808/IOBR")
```
```{r}
library('IOBR')
```

Main documentation is on the `deconvo_tme` function in the package:

- support methods
```{r}
tme_deconvolution_methods
```
- quick start
```{r eval=F, echo=T}
# Example
lm22<-deconvo_tme(eset = eset_crc, project = "TCGA-CRC", method = "cibersort", arrays = F)
```

subgroup survival analyses
```{r}
help("subgroup_survival")
##source data and filter NA
data(subgroup_data)
input <- subgroup_data %>% 
   filter(time > 0) %>% 
   filter(!is.na(status)) %>% 
   filter(!is.na(AJCC_stage))
dim(input)
##for binary variable
data1 <- subgroup_survival(pdata = input,
                           time ="time", 
                           status = "status",
                           variable = c("ProjectID", "AJCC_stage"), 
                           object ="score_binary" )
data1
```

References
---------
Contact:
E-mail any questions to dongqiangzeng0808@gmail.com
